Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-02-03 paper/paper-nature_format.tex
lots of updates

---
title: "Digitization of the Australian Parliamentary Debates, 1998-2022"
number-sections: true
format: 
  pdf:
    keep-tex: true
bibliography: references.bib
editor: visual
date: "now"
date-format: long
author:
  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
abstract: "Public knowledge of what is said in parliament is a key tenet of democracy, and a critical resource for political science research. In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard. While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality. Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard. The database is publicly available and can be readily linked to other datasets such as election results. The creation and accessibility of this database will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers."
---

```{r, echo=F, message=F}
library(here)
library(tidyverse)
library(XML)
```

# Background & Summary {#sec-intro}

The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, a team of researchers at the University of Toronto have digitized Hansard from 1901 to 2019, an endeavour called the Linked Parliamentary Data (LiPaD) project [@lipad]. Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling. Following the lead of the LiPaD project, in this paper we introduce a novel database for the Australian Hansard. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form which can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a valuable resource for efficiently studying and exploring political behaviour in Australia over time.

The House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch. 1]. The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber. Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch. 8]. A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch. 8]. The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber. This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch. 21]. Sittings in the Federation Chamber are quite different to those of the Chamber in terms of their order of business and scope of discussion. Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch. 21]. It is the recording and compilation of all of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.

A week or so after each sitting day, a transcript is available for download from the official Parliament of Australia website in both static PDF and extensible markup language (XML) form. The PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt]. This conversion allows for the production of the XML formatted transcript, though these are not always perfect conversions and are particularly flawed in the early decades of Hansard [@sherratt]. The PDF imposes formatting designed for humans to read with ease, whereas XML is designed for consistency and machine legibility. The nature of XML enables us to more easily use code to manipulate these records at scale, motivating our choice to develop our database solely using the XML formatted files. In cases where we were unsure on how to proceed with processing the XML, we defer first to the PDF, and then to the video recording of the proceeding if available.

At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis. To this point, various researchers have had to create their own databases in an attempt to produce usable, complete data based on content from the Australian Parliament website. For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files. These data can be navigated by year, parliament, people, and bills [@sherratt]. In an effort to make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all Members of the Australian House of Representatives from 1945 to 2019. Further, @auspol created the `AustralianPoliticians` `R` package, which contains a number of datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.

A number of papers exist which utilize components of Australian Hansard to explore various research topics. For example, @salisbury2011 used online Hansard records to investigate the occurrences of unparliamentary comments by members of the House, where The Speaker tells that member to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

# Methods

@@

## Overview {#sec-overview}

The approach to parsing contents of an XML document is heavily dependent on its tree structure. As such, to create this database, we started by looking at a single Hansard XML transcript from 2019. Doing so enabled us to identify the various components of interest in the document, and how each one can be parsed according to its corresponding structural form. Parsing was performed in `R` using the `XML` and `xml2` packages [@XML_pkg; @xml2_pkg]. Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible. The typical form of a Hansard XML transcript is summarized in the nested list below. Note that this provides a broad overview of the structure, and does not contain every possible nested element that may be found in a Hansard XML.

>          <hansard>
>            1. <session.header>
>            2. <chamber.xscript>
>               a)  <business.start>
>               b)  <debate>
>                   i.  <debateinfo>
>                   ii. <debate.text>
>                   iii. <speech>
>                   iv. <subdebate.1>
>                       (1) <subdebateinfo>
>                       (2) <subdebate.text>
>                       (3) <speech>
>                       (4) <subdebate.2>
>                           (a) <subdebateinfo>
>                           (b) <subdebate.text>
>                           (c) <speech>
>           3. <fedchamb.xscript>
>           4. <answers.to.questions>
>               a)  <question>
>               b)  <answer>

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. Note that the Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings of the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with a business start which is followed by a series of debates. Debate nodes can contain a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it. That said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the speaker and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@fig-xml1 provides an example of the beginning of an XML file for Hansard, which illustrates the structure outlined in the nested list above. As stated, the XML structure begins with a parent element `"hansard"` (highlighted in blue), followed by a child element `"session.header"` (highlighted in yellow) with sub-child elements such as the date and parliament number, which are all highlighted in pink. Next there is the child element containing everything that takes place in the Chamber, `"chamber.xscript"`, which is also highlighted in yellow in @fig-xml1. As previously mentioned, the first sub-node of `"chamber.xscript"` is the business start. The structure of the business start can be seen between the nodes highlighted in green in @fig-xml1, where the content we parse from the business start are highlighted in orange.

**does this feel a bit repetitive? do you think it's worth keeping?**

![Snapshot of beginning of XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}

Evidently, the nature of XML formatting means that different pieces of information are categorized under a series of uniquely named and nested nodes. As a result, to parse each piece of information, one must specify the unique hierarchy of nodes in which it is structured. This is known as an XPath expression, and tells the parser how to navigate the XML document to obtain the desired information. For example, the session header date in @fig-xml1 can be accessed using the XPath expression "`hansard/session.header/date`". We began our first script by parsing every piece of information contained in the XML document, using these unique XPath expressions to do so.

The next step was to further develop our script to produce tidy data sets containing each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order. This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort. @sec-interject will provide further details on the intricacies of this task.

@@

Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files. The earliest sitting day our first script can successfully parse is 14 August 2012. Before developing new scripts to parse earlier Hansard documents, we decided to prioritize cleaning and finalizing what we have been able to parse. As such we continued building our script, fixing any problems we noticed in the resulting datasets such as excess whitespace or spacing issues, and splitting up any additional sections of the parsed text onto separate rows where necessary. Specifically, we added a section of our script to separate out general stage directions. More information on this separation will be provided in @sec-stage. After completing our first script, it was formatted as a function which takes a single file name argument and produces one CSV file containing data on all proceedings from the given sitting day.

## Script Differences {#sec-diff}

As previously mentioned, we developed a total of four scripts to parse the 1998-2022 time frame of Hansard documents. Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts. While all four scripts use the same general approach to parsing described in @sec-overview and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.

The need for a second script stems from the fact that when established in 1994, the Federation Chamber was originally named the Main Committee. The Main Committee was renamed to the Federation Chamber in mid-2012 [@australia2018house, ch. 21]. As a result, the child-node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012. Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification. To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`. After making this modification and accounting for other small changes such as time stamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).

While the modifications needed to develop the second script were quite straightforward, this was not the case for our next script. The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology. In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`. The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments and continuations. After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order. For example, if the speech began, was interrupted by one member, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node. These would contain details on the person who made each statement such as their party and electorate.

In contrast, the speech contents in XMLs from 1998 up to and including 24 March 2011 are nested differently --- there is no `<talk.text>` node. Rather than this single child-node that contains all speech content, statements are categorized in individual child-nodes. This means that unlike our code for parsing more current Hansards, we cannot specify a single XPath expression such as "`debate/speech/talk.text`" or "`debate/subdebate.1/speech/talk.text`" to extract all speeches, in their entirety, at once. This difference in nesting structure made our second script unusable for parsing transcripts preceding 10 May 2011, and required us to change our data processing approach considerably.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Digitization of the Australian Parliamentary Debates, 1998-2022},
  pdfauthor={Lindsay Katz; Rohan Alexander},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{January 20, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a key tenet of
democracy, and a critical resource for political science research. In
Australia, following the British tradition, the written record of what
is said in parliament is known as Hansard. While the Australian Hansard
has always been publicly available, it has been difficult to use it for
the purpose of large-scale macro and micro-level text analysis because
it has not been available as a dataset of sufficient quality. Following
the lead of the Linked Parliamentary Data project which achieved this
for Canada, we provide a new, comprehensive, high-quality database that
captures all proceedings of the Australian parliamentary debates from
1998 to the present using Hansard. The database is publicly available
and can be readily linked to other datasets such as election results.
The creation and accessibility of this database will enable the
exploration of questions that are not currently possible to explore,
serving as a valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

\hypertarget{sec-intro}{%
\section{Background \& Summary}\label{sec-intro}}

The official written record of parliamentary debates, formally known as
Hansard, plays a fundamental role in capturing the history of political
proceedings and facilitating the exploration of valuable research
questions. Originating in the British parliament, the production of
Hansard became tradition in a number of Commonwealth countries such as
Canada, the United Kingdom, and Australia (Vice and Farrell 2017). Given
the content and magnitude of these records, they have significance,
particularly in the context of political science research. In the case
of Canada, a team of researchers at the University of Toronto have
digitized Hansard from 1901 to 2019, an endeavour called the Linked
Parliamentary Data (LiPaD) project (Beelen et al. 2017). Having a
digitized version of Hansard enables researchers to perform advanced
analyses on these records using text analysis tools and statistical
modelling. Following the lead of the LiPaD project, in this paper we
introduce a novel database for the Australian Hansard. This is composed
of individual datasets for each sitting day in the House of
Representatives from 1998 to 2022, containing details on everything said
in parliament in a form which can be readily used by researchers. With
the development of tools for large-scale text analysis, this database
will serve as a valuable resource for efficiently studying and exploring
political behaviour in Australia over time.

The House of Representatives performs a number of crucial governmental
functions, such as creating new laws and overseeing government
expenditure (House of Representatives 2018, ch.~1). The House operates
under a parallel chamber setup, meaning there are two debate venues
where proceedings take place: the Chamber, and the Federation Chamber.
Sittings of the House follow a predefined order of business, regulated
by procedural rules called standing orders (House of Representatives
2018, ch.~8). A typical sitting day in the Chamber has a number of
scheduled proceedings including debates on government business, 90
second member statements, and Question Time (House of Representatives
2018, ch.~8). The Federation Chamber was created in 1994 as a
subordinate debate venue of the Chamber. This allows for better time
management of House business as its proceedings occur simultaneously
with those of the Chamber (House of Representatives 2018, ch.~21).
Sittings in the Federation Chamber are quite different to those of the
Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members (House of Representatives 2018, ch.~21). It is the recording and
compilation of all of these proceedings on which Hansard is based, and
it is essentially, but not entirely, verbatim.

A week or so after each sitting day, a transcript is available for
download from the official Parliament of Australia website in both
static PDF and extensible markup language (XML) form. The PDF is the
official release, which is converted to typed text using Optical
Character Recognition (OCR) technology (Sherratt 2016). This conversion
allows for the production of the XML formatted transcript, though these
are not always perfect conversions and are particularly flawed in the
early decades of Hansard (Sherratt 2016). The PDF imposes formatting
designed for humans to read with ease, whereas XML is designed for
consistency and machine legibility. The nature of XML enables us to more
easily use code to manipulate these records at scale, motivating our
choice to develop our database solely using the XML formatted files. In
cases where we were unsure on how to proceed with processing the XML, we
defer first to the PDF, and then to the video recording of the
proceeding if available.

At present, the Hansard format that is available on the Parliament of
Australia website is not accessible for large scale analysis. To this
point, various researchers have had to create their own databases in an
attempt to produce usable, complete data based on content from the
Australian Parliament website. For instance, Sherratt (2016) created an
online, easy to read database of Hansard from 1901 to 1980 using the XML
files. These data can be navigated by year, parliament, people, and
bills (Sherratt 2016). In an effort to make the Australian Parliamentary
Handbook more accessible, Leslie (2021) has released an \texttt{R}
package which includes data on all Members of the Australian House of
Representatives from 1945 to 2019. Further, Alexander and Hodgetts
(2021) created the \texttt{AustralianPoliticians} \texttt{R} package,
which contains a number of datasets related to the political and
biographical information of Australian federal politicians who were
active between 1901 and 2021.

A number of papers exist which utilize components of Australian Hansard
to explore various research topics. For example, Salisbury (2011) used
online Hansard records to investigate the occurrences of unparliamentary
comments by members of the House, where The Speaker tells that member to
withdraw their remark. Rasiah (2010) worked with Question Time data from
Hansard transcripts during February and March of 2003, to investigate
resistance of politicians in answering questions about Iraq. In their
work, Fraussen, Graham, and Halpin (2018) use Hansard to quantify
political prominence by investigating strategic mentions of interest
groups by elected officials. Finally, the work of Alexander and
Alexander (2021) offers a dataset of the Australian Hansard, along with
an analysis of the effect of elections and changes in Prime Ministers
upon topics mentioned in parliament. Alexander and Alexander (2021)
created this database with the static PDF versions of Hansard, using OCR
to digitize these files into text which is suitable for analysis. This
means there are considerable digitization errors especially in the first
half of the dataset.

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{sec-overview}{%
\subsection{Overview}\label{sec-overview}}

The approach to parsing contents of an XML document is heavily dependent
on its tree structure. As such, to create this database, we started by
looking at a single Hansard XML transcript from 2019. Doing so enabled
us to identify the various components of interest in the document, and
how each one can be parsed according to its corresponding structural
form. Parsing was performed in \texttt{R} using the \texttt{XML} and
\texttt{xml2} packages (Temple Lang 2022; Wickham, Hester, and Ooms
2021). Focusing on one transcript also allowed us to ensure that all key
components of the transcript were being parsed and captured with as much
detail as possible. The typical form of a Hansard XML transcript is
summarized in the nested list below. Note that this provides a broad
overview of the structure, and does not contain every possible nested
element that may be found in a Hansard XML.

\begin{quote}
\begin{verbatim}
     <hansard>
       1. <session.header>
       2. <chamber.xscript>
          a)  <business.start>
          b)  <debate>
              i.  <debateinfo>
              ii. <debate.text>
              iii. <speech>
              iv. <subdebate.1>
                  (1) <subdebateinfo>
                  (2) <subdebate.text>
                  (3) <speech>
                  (4) <subdebate.2>
                      (a) <subdebateinfo>
                      (b) <subdebate.text>
                      (c) <speech>
      3. <fedchamb.xscript>
      4. <answers.to.questions>
          a)  <question>
          b)  <answer>
\end{verbatim}
\end{quote}

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child-nodes,
where the first child-node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. Note that the Federation Chamber does not meet on
every sitting day, so this child element is not present in every XML
file. The use of separate child nodes allows for the distinction of
proceedings of the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with a business start which is
followed by a series of debates. Debate nodes can contain a sub-debate 1
child-node which has a sub-debate 2 child-node nested within it. That
said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of
these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the speaker and the time of their first statement.
Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate
settings --- they are often composed of a series of interjections and
continuations. These statements are categorized under different
sub-nodes depending on their nature, such as
\texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will follow in Section~\ref{sec-qa}.

Figure~\ref{fig-xml1} provides an example of the beginning of an XML
file for Hansard, which illustrates the structure outlined in the nested
list above. As stated, the XML structure begins with a parent element
\texttt{"hansard"} (highlighted in blue), followed by a child element
\texttt{"session.header"} (highlighted in yellow) with sub-child
elements such as the date and parliament number, which are all
highlighted in pink. Next there is the child element containing
everything that takes place in the Chamber, \texttt{"chamber.xscript"},
which is also highlighted in yellow in Figure~\ref{fig-xml1}. As
previously mentioned, the first sub-node of \texttt{"chamber.xscript"}
is the business start. The structure of the business start can be seen
between the nodes highlighted in green in Figure~\ref{fig-xml1}, where
the content we parse from the business start are highlighted in orange.

\textbf{does this feel a bit repetitive? do you think it's worth
keeping?}

\begin{figure}

{\centering \includegraphics{xml1.png}

}

\caption{\label{fig-xml1}Snapshot of beginning of XML file for Hansard
on 25 February 2020}

\end{figure}

Evidently, the nature of XML formatting means that different pieces of
information are categorized under a series of uniquely named and nested
nodes. As a result, to parse each piece of information, one must specify
the unique hierarchy of nodes in which it is structured. This is known
as an XPath expression, and tells the parser how to navigate the XML
document to obtain the desired information. For example, the session
header date in Figure~\ref{fig-xml1} can be accessed using the XPath
expression ``\texttt{hansard/session.header/date}''. We began our first
script by parsing every piece of information contained in the XML
document, using these unique XPath expressions to do so.

The next step was to further develop our script to produce tidy data
sets containing each parsed element, where each statement is separated
onto its own row with details about the speaker, and rows are placed in
chronological order. This first involved correcting the variable classes
and adding a number of indicator variables to differentiate where
statements came from, such as Chamber versus Federation Chamber or
sub-debate 1 versus sub-debate 2. The next key task stemmed from the
fact that the raw text data were not separated by each statement when
parsed. In other words, any interjections, comments made by The Speaker
or Deputy Speaker and continuations within an individual speech were all
parsed together as a single string. As such, the name, name ID,
electorate and party details were only provided for the person whose
turn it was to speak. Splitting up these speeches in a way which would
be generalizable across sitting days required much thought and effort.
Section~\ref{sec-interject} will provide further details on the
intricacies of this task.

@@

Once the script ran without error for a few recent years of Hansard, we
continued to work backwards until extensive changes in tree structure
made our script incompatible with parsing earlier XML files. The
earliest sitting day our first script can successfully parse is 14
August 2012. Before developing new scripts to parse earlier Hansard
documents, we decided to prioritize cleaning and finalizing what we have
been able to parse. As such we continued building our script, fixing any
problems we noticed in the resulting datasets such as excess whitespace
or spacing issues, and splitting up any additional sections of the
parsed text onto separate rows where necessary. Specifically, we added a
section of our script to separate out general stage directions. More
information on this separation will be provided in
Section~\ref{sec-stage}. After completing our first script, it was
formatted as a function which takes a single file name argument and
produces one CSV file containing data on all proceedings from the given
sitting day.

\hypertarget{sec-diff}{%
\subsection{Script Differences}\label{sec-diff}}

As previously mentioned, we developed a total of four scripts to parse
the 1998-2022 time frame of Hansard documents. Two main factors
motivated us to create four scripts as opposed to just one, the first
being structural variation in XML over time, and the second being
improved computational efficiency with separate scripts. While all four
scripts use the same general approach to parsing described in
Section~\ref{sec-overview} and produce the same CSV structure, the first
and second scripts use a different method of data processing than the
third and fourth scripts.

The need for a second script stems from the fact that when established
in 1994, the Federation Chamber was originally named the Main Committee.
The Main Committee was renamed to the Federation Chamber in mid-2012
(House of Representatives 2018, ch.~21). As a result, the child-node
under which Federation Chamber proceedings are nested is named
\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
prior to 14 August 2012. Having developed our first script based on
Hansard from recent years, all XPath expressions contain the
\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
avoid causing issues in our first script which successfully parses about
10 years of Hansard, we created a second script where we replaced all
occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
modification and accounting for other small changes such as time stamp
formatting, this second script successfully parses all Hansard sitting
days from 10 May 2011 to 28 June 2012 (inclusive).

While the modifications needed to develop the second script were quite
straightforward, this was not the case for our next script. The typical
tree structure of Hansard XMLs spanning from 1998 to March 2011 has an
important difference from that of XMLs released after March 2011,
necessitating many changes to be made in our methodology. In XMLs after
March 2011, which our first two scripts successfully parse, the first
two child-nodes of \texttt{\textless{}speech\textgreater{}} are
typically \texttt{\textless{}talk.start\textgreater{}}, and
\texttt{\textless{}talk.text\textgreater{}}. The first child-node
contains data on the person whose turn it is to speak, and the second
contains the entire contents of that speech --- including all
interjections, comments and continuations. After the
\texttt{\textless{}talk.text\textgreater{}} element closes, there are
typically a series of other child-nodes which provide a skeleton
structure for how the speech proceedings went in chronological order.
For example, if the speech began, was interrupted by one member, and
then continued uninterrupted until the end, there would be one
\texttt{\textless{}interjection\textgreater{}} node and one
\texttt{\textless{}continuation\textgreater{}} node following the
\texttt{\textless{}talk.text\textgreater{}} node. These would contain
details on the person who made each statement such as their party and
electorate.
